Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-04-20 AppendixI.Rmd
Grphs

@@

```{r FigBayesianScheme,fig.cap="Scheme of the Bayesian process propagating the taxonomic uncertainty"}
knitr::include_graphics("ExternalFig/BayesianSheme.png")
```

```{r FigSeedMassClasses, echo=FALSE, out.width='100%', fig.asp=2/5,fig.cap="Trajectories of seed mass classes proportions over 30 years after disturbance, corresponding to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. No gap filling process was applied in this case. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.", fig.env="figure*"}
load("DB/Smass_ClassProp")

@@

>>>>

# Appendix figures

@@

**Figure A3**: Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes. \@ref(fig:DivFunAppendix).

\newpage

# Figure A1

```{r FigBayesianScheme,out.width='100%',fig.cap="Scheme of the Bayesian process propagating the taxonomic uncertainty",echo=F, fig.env="figure*"}
knitr::include_graphics("ExternalFig/BayesianSheme.png")
```

# Figure A2

```{r FigSeedMassClasses, echo=FALSE, out.width='80%', fig.asp=2/5,fig.cap="Trajectories of seed mass classes proportions over 30 years after disturbance, corresponding to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. No gap filling process was applied in this case. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.", fig.env="figure*"}
load("DB/Smass_ClassProp")

@@

# Figure A3

```{r DivFunAppendix, out.width = '60%', echo=FALSE, fig.cap="Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes.", fig.env="figure*"}
load("DB/FunctionalTraj_ForGraphsnew")

FunTraj(CompleteFun,remove=F)

### 2018-04-20 AppendixI.tex
Grphs

@@

\textbf{Figure A1}: Whenever the family or genus were recorded for a
vernacular name, the pool of species sampled to replace the vernacular
name was restricted to those pertaining to the same higher taxonomic
level (i.e species of the same genus when the species is missing,
species of the same family when the genus is missing).

\textbf{Figure A2}: Trajectories of seed mass classes proportions over
30 years after disturbance, corresponding to the median (solid line) and
0.025 and 0.975 percentile (gray envelope) observed after 50 iteration
of the taxonomic uncertainty propagation. No gap filling process was
applied in this case. Initial treatments are represented by solid lines
colors with green for control, blue for T1,orange for T2 and red for T3.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{include_graphics}\NormalTok{(}\StringTok{"ExternalFig/BayesianSheme.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}

{\centering \includegraphics{ExternalFig/BayesianSheme}

@@

\caption{Scheme of the Bayesian process propagating the taxonomic uncertainty}\label{fig:FigA1}
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth]{AppendixI_files/figure-latex/FigA2-1}

@@

\caption{Trajectories of seed mass classes proportions over 30 years after disturbance, corresponding to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. No gap filling process was applied in this case. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.}\label{fig:FigA2}
\end{figure*}

>>>>

\section{Appendix figures}\label{appendix-figures}

@@

\textbf{Figure A1}: Whenever the family or genus were recorded for a
vernacular name, the pool of species sampled to replace the vernacular
name was restricted to those pertaining to the same higher taxonomic
level (i.e species of the same genus when the species is missing,
species of the same family when the genus is missing)
\ref{fig:FigBayesianScheme}.

\textbf{Figure A2}: Trajectories of seed mass classes proportions over
30 years after disturbance, corresponding to the median (solid line) and
0.025 and 0.975 percentile (gray envelope) observed after 50 iteration
of the taxonomic uncertainty propagation. No gap filling process was
applied in this case. Initial treatments are represented by solid lines
colors with green for control, blue for T1,orange for T2 and red for T3
\ref{fig:FigSeedMassClasses}.

\textbf{Figure A3}: Trajectories of the Rao functional diversity over 30
years after disturbance. Trajectories correspond to the median (solid
line) and 0.025 and 0.975 percentile (gray envelope) observed after 50
iteration of the taxonomic uncertainty propagation. Initial treatments
are represented by solid lines colorswith green for control, blue for
T1,orange for T2 and red for T3.and the missing trait value filling
processes. \ref{fig:DivFunAppendix}.

\newpage

\section{Figure A1}\label{figure-a1}

{\centering \includegraphics[width=1\linewidth]{ExternalFig/BayesianSheme}

@@

\caption{Scheme of the Bayesian process propagating the taxonomic uncertainty}\label{fig:FigBayesianScheme}
\end{figure*}

\section{Figure A2}\label{figure-a2}

@@

{\centering \includegraphics[width=0.8\linewidth]{AppendixI_files/figure-latex/FigSeedMassClasses-1}

@@

\caption{Trajectories of seed mass classes proportions over 30 years after disturbance, corresponding to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. No gap filling process was applied in this case. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.}\label{fig:FigSeedMassClasses}
\end{figure*}

\section{Figure A3}\label{figure-a3}

{\centering \includegraphics[width=0.6\linewidth]{AppendixI_files/figure-latex/DivFunAppendix-1}

\caption{Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes.}\label{fig:DivFunAppendix}
\end{figure*}

### 2018-04-20 WholePlotTrajectories.Rmd
Grphs

For all undisturbed plots the Rao diversity remained comparable to the initial values, 5 years after disturbance (1989 inventories).
The trajectories of all disturbed plots followed a unimodal trajectory with a maximum positively correlated to disturbance intensity ($\rho_{spearman}$) (Figure \@ref(fig:DivFun)). 
Thirty years after disturbance all plots, whenever the initial disturbance intensity, regained diversity values similar to their initial avule and to those of control plots.

```{r DivFun, out.width = '100%', echo=FALSE, fig.cap="Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes."}
load("DB/FunctionalTraj_ForGraphs")

FunTraj(CompleteFun)

@@

The monitoring 30 years of disturbed forest communities confirmed the limited direct impact of low disturbance on species richness as it was found for impact survey of selective logging [@Cannon1998;@Baraloto2012a].
Only the most disturbed plots had not fully achieved the ongoing recovery of genus richness, although all had already reached equivalent levels as those of some control plots.
Such long time richness recovery had already been observed in several logging experiments, which also highlighted the role of random disturbance damage in the richness decrease [@deAvila2015;@Hu2018].

>>>>

For all undisturbed plots the Rao diversity remained comparable to the initial values, 5 years after disturbance (1989 inventories).
The trajectories of all disturbed plots followed a unimodal trajectory with a maximum positively correlated to disturbance intensity ($\rho_{spearman}$) (Figure \@ref(fig:DivFun)). 
The plot 7 from treatment 1 was removed from the graphical representation for better readability, see appendix for full graph.
Thirty years after disturbance all plots, whenever the initial disturbance intensity, regained diversity values similar to their initial avule and to those of control plots.

```{r DivFun, out.width = '100%', echo=FALSE, fig.cap="Trajectories of the Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colorswith green for control, blue for T1,orange for T2 and red for T3.and the missing trait value filling processes."}
load("DB/FunctionalTraj_ForGraphsnew")

FunTraj(CompleteFun,remove=T)

@@

The monitoring 30 years of disturbed forest communities confirmed the limited direct impact of low disturbance on species richness as it was found for impact survey of selective logging [@Cannon1998;@Baraloto2012a].
Only the most disturbed plots had not fully achieved the ongoing recovery of genus richness, although all had already reached equivalent levels as those of some control plots.
Such long time richness recovery had already been observed in several logging experiments, which also highlighted the role of random disturbance damage in the richness decrease [@DeAvila2015;@Hu2018].

### 2018-04-20 WholePlotTrajectories.tex
Grphs

For all undisturbed plots the Rao diversity remained comparable to the
initial values, 5 years after disturbance (1989 inventories). The
trajectories of all disturbed plots followed a unimodal trajectory with
a maximum positively correlated to disturbance intensity
(\(\rho_{spearman}\)) (Figure \ref{fig:DivFun}). Thirty years after
disturbance all plots, whenever the initial disturbance intensity,
regained diversity values similar to their initial avule and to those of
control plots.

@@

The monitoring 30 years of disturbed forest communities confirmed the
limited direct impact of low disturbance on species richness as it was
found for impact survey of selective logging
\citep{Cannon1998, Baraloto2012a}. Only the most disturbed plots had not
fully achieved the ongoing recovery of genus richness, although all had
already reached equivalent levels as those of some control plots. Such
long time richness recovery had already been observed in several logging
experiments, which also highlighted the role of random disturbance
damage in the richness decrease \citep{deAvila2015, Hu2018}.

>>>>

For all undisturbed plots the Rao diversity remained comparable to the
initial values, 5 years after disturbance (1989 inventories). The
trajectories of all disturbed plots followed a unimodal trajectory with
a maximum positively correlated to disturbance intensity
(\(\rho_{spearman}\)) (Figure \ref{fig:DivFun}). The plot 7 from
treatment 1 was removed from the graphical representation for better
readability, see appendix for full graph. Thirty years after disturbance
all plots, whenever the initial disturbance intensity, regained
diversity values similar to their initial avule and to those of control
plots.

@@

The monitoring 30 years of disturbed forest communities confirmed the
limited direct impact of low disturbance on species richness as it was
found for impact survey of selective logging
\citep{Cannon1998, Baraloto2012a}. Only the most disturbed plots had not
fully achieved the ongoing recovery of genus richness, although all had
already reached equivalent levels as those of some control plots. Such
long time richness recovery had already been observed in several logging
experiments, which also highlighted the role of random disturbance
damage in the richness decrease \citep{DeAvila2015, Hu2018}.
